Vulnerability Analysis of Container Images in Neuroimaging

### 2020-05-19 paper.tex
changed intro

To answer that question, we scan images that are used on Compute
Canada clusters by neuroscience field. Scanning refers to the practice of
collecting all information about the container image, investigating it
for vulnerabilities, and finally producing a
report to summarize scanning results. It is broadly categorized into
two types: static scanning and dynamic scanning. The former scanning technique
involves extracting information of an image without running it into a container,
whereas the latter approach involves launching the container from the target image, and
then scanning the running container.
Here, we focus mainly on vulnerability scanning.
Vulnerability is a weakness in the developer's software that can be used
by the attacker to perform unathorized actions on the target computer.
In this paper, we report all vulnerabilities that are present in
container images, specifically used by neuroimaging field. Particularly,
we aim to answer four primary research questions:

@@

To answer those questions, we take an example of neuroscience field where
containers are used on Compute Canada HPC cluster.
The existing research work on containers focuses mainly on the security of Docker
containers.
This focus is justified by the fact that, containers expose the host's resources
(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
threat for the applications running on the same host. Previous studies evaluated
security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
Also Singularity came up with Stools, which can be used for scanning Singularity images
for security and quality checks.
Here, we focus on the specific context of scientific data analysis on HPC clusters, taking
neuroimaging as an example.

This paper is organized as follows: in next section, we provide description
of materials and methods which includes summarizing a particular use case of
containers in neuroscience, which is used for scientific computing. It involves
usage of containers on shared HPC cluster. Additionally, in this section we
describe all the resources that are used by this use case. We also explain
scanning tools that we use for scanning container images to report
vulnerabilities. Next section of this paper is about the results. Here, we
present number and type of vulnerabilites that are present in the container images
which are used for data analysis on shared HPC clusters, and discuss how many of them are
critical vulnerabilities. Following section is about discussion of these results
where we provide more insight into the risks that are caused by these vulnerabilties
and how they can be leveraged to design attacks. Here, we also provide some such
vulnerability examples. Finally, we conclude this paper by discussing ten simple
rules that can be followed to secure container image for use in clusters.

@@

This study involves three image scanning experiments.
The first experiment scans the images as is to report the existing vulnerabilities
inside the images. The scan report of
these images shows a large number of existing vulnerabilities which may pose
a potential security risk. These vulnerabilities exist due to the outdated
packages that are present inside the images. So, the next step is to
take the necessary steps to improve security in the images. Therefore, there exist
two possible solutions.
The first one involves updating
all these images and then rescanning them, which constitutes the second experiment of our study. The next 
experiment involves shrinking the size of the image
meaning that removing all unnecessary packages from the image to see the effect on the number of
vulnerabilities present inside the image, which will be presented as our third experiment.

We first
introduce two container tools used in our experiments: Docker and
Singularity and their image formats. Then we describe Boutiques and BIDS application frameworks
from where we took containerized applications for our study. 
Later, this section
presents two scanning techniques followed by a description of image scanners used.
In this study, we used three different image scanners because they
use different scanning techniques and/or refer to different vulnerability sources.
The images used in our study have different Linux distributions/releases, which have
different vulnerability data. Therefore, in the last, this section presents a
description of these varying Linux distributions/releases and their
vulnerability databases.

\begin{comment}
As we are taking a particular use case of containers from
neuroscience field i.e Canadian Open Neuroscoence Platform (CONP) so  
in this section we summarize the data and tools 
that are used in CONP. CONP is a national platform for sharing neuroscience
research data and aims at creating an interactive interface for neuroscientists and
clinical neuroscience. The main goal of the CONP platform is to store, process, and
distribute massive amounts of data produced by modern neuroscience.
Here, we summarize all the resources that are
used by CONP to function.
\end{comment}

@@

\begin{comment}
consists of the following three main components:

\textit{Docker Daemon:} It acts as a server. It is
a long-running process that manages all Docker images, containers, storage volumes, and networks.

\textit{REST API:} It acts as an interface between the server and the client, and is an API which is used by the applications
to talk to the \textit{Docker Daemon}.

\textit{Client:} It is a Command Line Interface (CLI) client which is used to interact with the \textit{Docker Daemon}.
convert english to punjabi
\end{comment}
%Docker runs a software, \textit{Docker daemon}, on the host machine.
It runs as root and is remotely controlled through a
UNIX socket. It is responsible for launching and managing containers,
consequently, when a container runs, the container is spawned as a
child process of this root-owned daemon.

@@

\begin{comment}
Singularity offers mobility of compute by facilitating portable environments 
through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
is created, it is hashed using SHA-256. Hence, it cannot be changed
once it is created, consequently, it can be used for reproducing the results of
scientific experiments. Main features provided by
Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
We used Singularity version $2.5.2$ in our experiments.
Users can easily access files, devices, sockets, ports of the host system from
the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
into the running container. Additional directories can be specified with \textit{--bind}
to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
However namespaces can be requested if required. Users cannot escalate privileges inside
Singularty containers. This is because Singularity do not run containers as root.
Instead, a user inside Singularity container is the same user outside the container.

\subsection{Container Image Formats}

A container image is a package that contains an application along with its
required dependencies and libraries.
Both, Docker and Singularity, have different image formats. Below we provide a description of both image
formats.

\subsubsection{Docker Image Format}

Docker images are organized as a series of layers stacked on top of each
other and identified by unique layer identifiers. If a layer is reused
in different images it will
have the same id across images. Each layer consists of a filesystem diff
with respect to the layer below. 
DockerHub uses gzip compression for
transferring layers.There are two ways to create a Docker image. The
first is to use an existing Docker image as a base image and then build a
new image from that one, by making changes in the filesystem, which is
saved as a new layer of the Docker image. The second way is to build a new
Docker image from scratch.Docker supports several different storage drivers.
\textit{Overlay2} is the preferred storage driver used by Docker for all currently
supported Linux versions, whereas \textit{aufs} is preferred for Docker 18.06 and
older, when using Ubuntu 14.04 on kernel 3.13 as it do not support \textit{overlay2}.
Other storage drivers that are supported by Docker include \textit{devicemapper, btrfs,
zfs, and vfs}

\subsubsection{Singularity Image Format}

On the other hand, a Singularity image is a single immutable file and 
does not contain layers.
Once a Singularity image is created, it cannot be changed, consequently,
it can be used for reproducing the results of scientific
experiments.
Singularity takes snapshot, locks, and archives the developed application,
which is known as Singularity image.
It means that Singularity image is a single immutable file that can be moved around as
any other file. This file can be checksummed, signed, and easily
used for verification purposes. Singularity containers use Squashfs file format
by default. It is read-only file system in Linux, which uses compression for files,
inodes, and directories. However, Singularity also supports two other 
formats i.e \textit{sandbox} format
(which is just a chroot
directory) and \textit{writable} format (the ext3 file system).
While publishing experimental results, authors can also publish Singularity
image along with its hash, which allow other researchers to verify results.
\end{comment}
\subsection{Application frameworks}

@@

Boutiques~\cite{glatard2018boutiques} is an application sharing system to
publish, integrate, and execute command-line applications across different
platforms. In Boutiques, the command-line of the application is described
through a flexible JSON descriptor pointing to a Docker or a Singularity
image where the application is installed. A set of core tools help
construct, validate, publish and execute Boutiques descriptors. Boutiques
applications are published on the Zenodo research repository.

We used the 49 Boutiques applications published on Zenodo at the time of
the writing. These applications use 23 different container images. Out of these images,
3 images are not found and 2 images were already included in BIDS images.
Therefore we are left with a total 18 Boutiques images which include 6
Singularity images and 12 Docker images.

@@

BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
analysis pipelines. It improves usability, accesibility, and reproducibility
of different applications through containerization.
At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
Out of these 27 images, we used 26 images for our experiments because the QAP bids app was not available
on Docker hub.
\end{comment}
So we have a total 38 Docker images from both BIDS Apps and Boutiques.
	Table~\ref{table1} displays the names of all the images that we took in our experiments.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

Scanning an image means looking into the image, collecting all the information about the image, and
finally, using this information to detect vulnerabilities present inside the image.
Scanning can be broadly categorized into two types: \rom{1}) Static Scanning and \rom{2})
Dynamic Scanning.
In Static scanning, an image is scanned without running it into a container. In respect to that,
different image features are extracted like installed packages, their versions, files, etc.
On the other hand, Dynamic scanning involves running a container from the image and then scanning the
dynamic behavior of the image.

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
Using a dynamic scanning technique, it offers
remote and local scans. The remote scan involves setting up only one machine, to
which other target servers are connected via SSH. Local scan involves running
the scan on the target server itself. Further, Vuls offer a fast scan, fast root scan,
and deep scan.
The Fast scan is performed without root privileges, whereas a fast root scan is
performed with root privileges. The latter also uses checkrestart utility to 
detect processes that are updated but not yet restarted because if they are not
restarted, updates are not effective. So fast root scan also detects these
processes. Both fast scan and fast root scan are performed offline without Internet
access, and put almost no load on the scan target server. The Deep scan uses
root privileges for scanning and is used to get a more detailed scan. It checks
changelogs, which puts more load on the target server.
Vuls gets data from Open Vulnerability and Assessment Language (OVAL).

The interesting point is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
meaning that images with these distributions are impossible to scan with Vuls.

@@

CoreOS originally created Clair, a static vulnerability scanner for containers. 
\begin{comment}
The main goal of the
tool is to provide a transparent look of container’s security. Clair scans container images in regular
intervals, and stores metadata of vulnerabilities, after getting from configured
set of sources. 
\end{comment}	
Clair API can be used by clients to query its database to get
the list of vulnerabilities that a particular image has. Clair sends a notification
to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
is a registry to store images privately, uses Clair internally as the security engine. However, Clair does not 
provide the facility for comparing
the vulnerability list of a particular image against a whitelist of vulnerabilities that you
want to ignore~\cite{arminc_2019}. 
So, to remove
that drawback, another tool from CoreOS, Clair Scanner can be used. It scans the image, prepares the list of
vulnerabilities, compares that list against the whitelist, and flags vulnerabilities
that are not present in the whitelist.
Clair Scanner refers to the Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
For that purpose, a Docker image is maintained that contains the Ubuntu CVE tracker database.
Whenever Ubuntu updated its database, this image is also updated with the required information.

@@

\href{https://github.com/singularityhub/stools}{Stools} combines CoreOS's Clair Scanner with Continuous Integration (CI)
for scanning Singularity images for vulnerabilities.
Initially, Clair Scanner was intended to scan Docker Containers. This tool does not fit well
to scan Singularity images because of the different image formats.
However, TravisCI and CircleCI are commonly used for testing code, and these
services also offer running containers. So Stools combined both the concepts.
It involves spinning a Clair Scanner container during testing and building a
Singularity image, and scanning it for filesystem before the image is finalized.

@@

>>>>

To answer that question, we scan images that are used on Compute
Canada clusters by neuroscience field. Scanning refers to the practice of
collecting all information about the container image, investigating it
for vulnerabilities, and finally producing a
report to summarize scanning results. It is broadly categorized into
two types: static scanning and dynamic scanning. The former scanning technique
involves extracting information of an image without running it into a container,
whereas the latter approach involves launching the container from the target image, and
then scanning the running container.
Here, we focus mainly on vulnerability scanning.
Vulnerability is a weakness in the developer's software that can be exploited
by the attacker to perform unathorized actions on the target computer.
In this paper, we report all vulnerabilities that are present in
container images, specifically used by neuroimaging field. Particularly,
we aim to answer four primary research questions:

@@

To answer those questions, we take an example of neuroscience field where
containers are used on Compute Canada HPC cluster.

The existing research work on containers focuses mainly on the security of Docker
containers.
This focus is justified by the fact that, containers expose the host's resources
(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
threat for the applications running on the same host. Previous studies evaluated
security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
Also Singularity came up with Stools, which can be used for scanning Singularity images
for security and quality checks.
Here, we focus on the specific context of scientific data analysis on HPC clusters, taking
neuroimaging as an example.

This paper is organized as follows: in next section, we provide description
of materials and methods which summarizes our four main experiments. We also explain
scanning tools that we use for scanning container images to report
vulnerabilities. Next section of this paper is about the results. Here, we
present number of vulnerabilites that are present in the container images
which are used for data analysis on shared HPC clusters. Following section is about 
discussion of these results where we provide more insight into the problems that 
we faced while conducting these experiments. Finally, we conclude this paper by discussing ten simple
rules that can be followed to secure container images for use in clusters.

@@

This study involves four image scanning experiments.
The first experiment scans the images as is to report the existing vulnerabilities
inside the images. The scan report of
these images shows a large number of existing vulnerabilities which may pose
a potential security risk. These vulnerabilities exist due to the outdated
packages that are present inside the images. So, the next step is to
take the necessary steps to improve security in the images. Therefore, there exist
two possible solutions.
The first one involves updating
all these images and then rescanning them, which constitutes the second experiment of our study. The next 
experiment involves shrinking the size of the image
meaning that removing all unnecessary packages from the image to see the effect on the number of
vulnerabilities present inside the image, which will be presented as our third experiment.
Lastly, our fourth experiment involves both updating and shrinking the image size and then
rescanning for the vulnerabilities.

Here, we first
introduce two container tools used in our experiments: Docker and
Singularity and their image formats. Then we describe Boutiques and BIDS application frameworks
from where we took containerized applications for our study. 
Later, this section
presents two scanning techniques followed by a description of image scanners used.
In this study, we used three different image scanners because they
use different scanning techniques and/or refer to different vulnerability sources.
The images used in our study have different Linux distributions/releases, which have
different vulnerability data. Therefore, in the last, this section presents a
description of these varying Linux distributions/releases and their
vulnerability databases.

%As we are taking a particular use case of containers from
%neuroscience field i.e Canadian Open Neuroscoence Platform (CONP) so  
%in this section we summarize the data and tools 
%that are used in CONP. CONP is a national platform for sharing neuroscience
%research data and aims at creating an interactive interface for neuroscientists and
%clinical neuroscience. The main goal of the CONP platform is to store, process, and
%distribute massive amounts of data produced by modern neuroscience.
%Here, we summarize all the resources that are
%used by CONP to function.

@@

%consists of the following three main components: 
%
%\textit{Docker Daemon:} It acts as a server. It is
%a long-running process that manages all Docker images, containers, storage volumes, and networks.
%
%\textit{REST API:} It acts as an interface between the server and the client, and is an API which is used by the applications
%to talk to the \textit{Docker Daemon}.
%
%\textit{Client:} It is a Command Line Interface (CLI) client which is used to interact with the \textit{Docker Daemon}.
%Docker runs a software, \textit{Docker daemon}, on the host machine.
It runs as root and is remotely controlled through a
UNIX socket. It is responsible for launching and managing containers,
consequently, when a container runs, the container is spawned as a
child process of this root-owned daemon.

@@

%\begin{comment}
%Singularity offers mobility of compute by facilitating portable environments 
%through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
%is created, it is hashed using SHA-256. Hence, it cannot be changed
%once it is created, consequently, it can be used for reproducing the results of
%scientific experiments. Main features provided by
%Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
%We used Singularity version $2.5.2$ in our experiments.
%Users can easily access files, devices, sockets, ports of the host system from
%the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
%into the running container. Additional directories can be specified with \textit{--bind}
%to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
%However namespaces can be requested if required. Users cannot escalate privileges inside
%Singularty containers. This is because Singularity do not run containers as root.
%Instead, a user inside Singularity container is the same user outside the container.
%
%\subsection{Container Image Formats}
%
%A container image is a package that contains an application along with its
%required dependencies and libraries.
%Both, Docker and Singularity, have different image formats. Below we provide a description of both image
%formats.
%
%\subsubsection{Docker Image Format}
%
%Docker images are organized as a series of layers stacked on top of each
%other and identified by unique layer identifiers. If a layer is reused
%in different images it will
%have the same id across images. Each layer consists of a filesystem diff
%with respect to the layer below. 
%DockerHub uses gzip compression for
%transferring layers.There are two ways to create a Docker image. The
%first is to use an existing Docker image as a base image and then build a
%new image from that one, by making changes in the filesystem, which is
%saved as a new layer of the Docker image. The second way is to build a new
%Docker image from scratch.Docker supports several different storage drivers.
%\textit{Overlay2} is the preferred storage driver used by Docker for all currently
%supported Linux versions, whereas \textit{aufs} is preferred for Docker 18.06 and
%older, when using Ubuntu 14.04 on kernel 3.13 as it do not support \textit{overlay2}.
%Other storage drivers that are supported by Docker include \textit{devicemapper, btrfs,
%zfs, and vfs}
%
%\subsubsection{Singularity Image Format}
%
%On the other hand, a Singularity image is a single immutable file and 
%does not contain layers.
%Once a Singularity image is created, it cannot be changed, consequently,
%it can be used for reproducing the results of scientific
%experiments.
%Singularity takes snapshot, locks, and archives the developed application,
%which is known as Singularity image.
%It means that Singularity image is a single immutable file that can be moved around as
%any other file. This file can be checksummed, signed, and easily
%used for verification purposes. Singularity containers use Squashfs file format
%by default. It is read-only file system in Linux, which uses compression for files,
%inodes, and directories. However, Singularity also supports two other 
%formats i.e \textit{sandbox} format
%(which is just a chroot
%directory) and \textit{writable} format (the ext3 file system).
%While publishing experimental results, authors can also publish Singularity
%image along with its hash, which allow other researchers to verify results.
%\end{comment}
\subsection{Application frameworks}

@@

Boutiques~\cite{glatard2018boutiques} is an application sharing system to
publish, integrate, and execute command-line applications across different
platforms. In Boutiques, the command-line of the application is described
through a flexible JSON descriptor pointing to a Docker or a Singularity
image where the application is installed. A set of core tools help
construct, validate, publish, and execute Boutiques descriptors. Boutiques
applications are published on the Zenodo research repository.

We used 49 Boutiques applications published on Zenodo at the time of
the writing. These applications use 23 different container images. Out of these images,
we could not get 3 images and 2 images were already included in BIDS images.
Therefore we are left with a total 18 Boutiques images which include 6
Singularity images and 12 Docker images.

@@

BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
analysis pipelines. It improves usability, accesibility, and reproducibility
of different applications through containerization.
At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
Out of these 27 images, we used 26 images for our experiments because the QAP bids app was not available
on Docker hub.
\end{comment}
So we have a total 38 Docker images from both BIDS Apps and Boutiques.
	Table~\ref{table1} displays the names of all the images that we took in our experiments.
Table~\ref{sing} lists 6 Singularity images taken from Boutiques framework.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

Scanning an image means looking into the image, collecting all the information about the image, and
finally, using this information to detect vulnerabilities present inside the image.
Scanning can be broadly categorized into two types: \rom{1}) Static Scanning and \rom{2})
Dynamic Scanning.
In Static scanning, an image is scanned without running it into a container. In respect to that,
different image features are extracted like installed packages, their versions, files, etc. to list
the vulnerabilities present inside the image.
On the other hand, Dynamic scanning involves running a container from the image and then scanning the
dynamic behavior of the image.

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
Using a dynamic scanning technique, it offers
remote and local scans at the time of writing. The remote scan involves setting up only one machine, to
which other target servers are connected via SSH. Local scan involves running
the scan on the target server itself. Further, Vuls offer a fast scan, fast root scan,
and deep scan mode.
The Fast scan is performed without root privileges, whereas a fast root scan is
performed with root privileges. The latter also uses checkrestart utility to 
detect processes that are updated but not yet restarted because if they are not
restarted, updates are not effective. So fast root scan also detects these
processes. Both fast scan and fast root scan are performed offline without Internet
access, and put almost no load on the scan target server. The Deep scan uses
root privileges for scanning and is used to get a more detailed scan. It checks
changelogs, which puts more load on the target server.

In our experiments, we used Vuls Docker image having version v0.9.0 with fast scan mode.
Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
The interesting point is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
meaning that images with these distributions are impossible to scan with Vuls.

@@

CoreOS originally created Clair, a static vulnerability scanner for containers. 
\begin{comment}
The main goal of the
tool is to provide a transparent look of container’s security. Clair scans container images in regular
intervals, and stores metadata of vulnerabilities, after getting from configured
set of sources. 
\end{comment}	
Clair API can be used by clients to query its database to get
the list of vulnerabilities that a particular image has. Clair sends a notification
to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
is a registry to store images privately, uses Clair internally as the security engine. However, Clair does not 
provide the facility for comparing
the vulnerability list of a particular image against a whitelist of vulnerabilities that you
want to ignore~\cite{arminc_2019}. 
So, to remove
that drawback, another tool from CoreOS, Clair Scanner can be used. It scans the image, prepares the list of
vulnerabilities, compares that list against the whitelist, and flags vulnerabilities
that are not present in the whitelist.
Clair Scanner refers to the Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
For that purpose, a Docker image is maintained that contains the Ubuntu CVE tracker database.
Whenever Ubuntu updates its database, this image is also updated with the required information.

@@

\href{https://github.com/singularityhub/stools}{Stools} combines CoreOS's Clair Scanner with Continuous Integration (CI)
for scanning Singularity images for vulnerabilities.
Initially, Clair Scanner was intended to scan Docker containers only. This tool does not fit well
to scan Singularity images because of the different image formats.
However, TravisCI and CircleCI are commonly used for testing code, and these
services also offer running containers. So Stools combined both the concepts.
It involves spinning a Clair Scanner container during testing and building a
Singularity image, and scanning it for filesystem before the image is finalized.

@@

\begin{table}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\columnwidth},
  after reading=\end{adjustbox},
 tabular={c |c},
        table head =Singularity Images & {Vulnerabilities by Stools}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{Singularityresults.csv}{}{\csvlinetotablerow}%
       \centering
        \caption{\label{sing}Number of Vulnerabilities in Singularity images}
\end{table}
